Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2020-07-30 papers/paper/paper.tex
remove obsolete todo and unsrt the bibliography

\section{To do items}

\subsection{Anyone tasks}
\begin{enumerate}
\item Movie of dynein walking as a supplemental figure
\end{enumerate}

\subsection{John}
\begin{enumerate}
\item Proofread the algorithm description, improve its writing, and
  check against code.
\item Run a low-ATP simulation for comparison data.
\item Consider a no-binding simulation and a separable model.  Create
  a figure demonstrating/testing whether the histogram of final
  displacement is independent of initial displacement.
\item Consider a simple Monte Carlo that just uses our no-unbinding
  and no-binding simulations to model dynein (like Yildiz).
\item Debug initial/final displacement plot - it looks like there's a weird
  threshold at final displacement = 0, is that normal?
\end{enumerate}

@@

\bibliographystyle{plain}
\bibliography{paper}

>>>>

@@

\bibliographystyle{unsrt}
\bibliography{paper}
